### 2016-09-28 projects_that_depend_on_sympy.tex

\href{http://sympygamma.com/}{\textbf{SymPy Gamma}} & An open source
  analog of Wolfram|Alpha that uses SymPy~\cite{SymPyGamma}.  See more in the supplementary material. \\

\href{http://cadabra.science/index.html}{\textbf{Cadabra}} &
  CAS designed specifically for the resolution of problems
  encountered in field theory~\cite{Peeters2007cadabra}. \\

@@

\href{https://github.com/jverzani/SymPy.jl}{\textbf{SymPy.jl}} &
  Provides a Julia interface to SymPy using PyCall~\cite{SymPy.jl}. \\

@@

\href{http://mathpix.com/}{\textbf{Mathpix}} & An iOS App, that detects handwritten math as input, and uses
  SymPy Gamma to evaluate the math input and generate the relevant
  steps to solve the problem~\cite{Mathpix}. \\

\href{http://openrave.org/docs/latest_stable/openravepy/ikfast/}{\textbf{IKFast}} &
  IKFast is a robot kinematics compiler provided by
  \href{http://openrave.org/}{OpenRAVE}~\cite{diankov2010ikfast}. \\

\href{http://www.sagemath.org/}{\textbf{SageMath}} &
  A free open-source mathematics software system, builds on top of many
  existing open-source packages, including SymPy~\cite{sagemath}. \\

@@

\href{http://yt-project.org/}{\textbf{yt}} & Python package for
  analyzing and visualizing volumetric data~\cite{2011ApJS..192....9T}. \\

\href{http://sfepy.org/}{\textbf{SfePy}} &
  A Python package for solving partial
  differential equations (PDEs) in 1D, 2D and 3D by the finite element (FE)
  method~\cite{Zienkiewicz2013FEM,cimrman2014sfepy}. \\

@@

\href{http://lcapy.elec.canterbury.ac.nz/}{\textbf{Lcapy}} &
  Experimental Python package for teaching linear circuit analysis~\cite{lcapy}. \\
\bottomrule
\end{longtable}

>>>>

\href{http://sympygamma.com/}{\textbf{SymPy Gamma}} & An open source
  analog of Wolfram|Alpha that uses SymPy~\cite{SymPyGamma}.  There is more
  information about SymPy Gamma supplementary material. \\

\href{http://cadabra.science/index.html}{\textbf{Cadabra}} &
  A CAS designed specifically for the resolution of problems
  encountered in field theory~\cite{Peeters2007cadabra}. \\

@@

\href{https://github.com/jverzani/SymPy.jl}{\textbf{SymPy.jl}} &
  A Julia interface to SymPy, provided using PyCall~\cite{SymPy.jl}. \\

@@

\href{http://mathpix.com/}{\textbf{Mathpix}} & An iOS App that detects handwritten math as input and uses
  SymPy Gamma to evaluate the math input and generate the relevant
  steps to solve the problem~\cite{Mathpix}. \\

\href{http://openrave.org/docs/latest_stable/openravepy/ikfast/}{\textbf{IKFast}} &
  A robot kinematics compiler provided by
  \href{http://openrave.org/}{OpenRAVE}~\cite{diankov2010ikfast}. \\

\href{http://www.sagemath.org/}{\textbf{SageMath}} &
  A free open-source mathematics software system, which builds on top of many
  existing open-source packages, including SymPy~\cite{sagemath}. \\

@@

\href{http://yt-project.org/}{\textbf{yt}} & A Python package for
  analyzing and visualizing volumetric data~\cite{2011ApJS..192....9T}. \\

\href{http://sfepy.org/}{\textbf{SfePy}} &
  A Python package for solving partial
  differential equations (PDEs) in 1D, 2D, and 3D by the finite element (FE)
  method~\cite{Zienkiewicz2013FEM,cimrman2014sfepy}. \\

@@

\href{http://lcapy.elec.canterbury.ac.nz/}{\textbf{Lcapy}} &
  An experimental Python package for teaching linear circuit analysis~\cite{lcapy}. \\
\bottomrule
\end{longtable}
